Pillar 1 - Sequential Pattern Mining

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
minor change

### Grade
```{r transactions expanded}

@@

  # Gather along rounded grades
  gather(
    key   = grade_ceil,
    value = X,
    `0`, `1`, `2`, `3`, `4`, `5`, `6`, `7`, `8`, `9`, `10`, 
    na.rm   = TRUE, 
    convert = TRUE
    ) %>%
  select(
    -X
    ) %>%

>>>>

### Grade
```{r transactions grade}

@@

  # Gather along rounded grades
  gather(
    key   = grade_ceil,
    value = X,
    `0` :`10`, 
    na.rm   = TRUE, 
    convert = TRUE
    ) %>%
  select(
    -X
    ) %>%
